---
title: "lab 5"
author: "Sam Rozal"
date: "10/25/2021"
output: 
  html_document: 
    toc: yes
    theme: cerulean
    code_folding: hide
---

```{r setup, include=FALSE, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals 

In this section, we'll use the `t.test()` function to calculate confidence intervals 

### Example 1

Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn to about in-line code referencing so our code becomes more reproducable 

```{r}
#create a mock sample
otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29, 90, 72, 112)

#Find the confidence intervals:
otter_ci <- t.test(otter_lengths)

#find the standard Deviation 
otter_sd <- sd(otter_lengths)
```
What does confidence interval mean?
- We would expect if we took multiple samples from this pop and calculated a confidence interval for each othem we expect for 95% of the confidence intervals to contain the true population mean. 


Mean otter leangth is 36.9 inches $\pm$ (mean $\pm$ n=8) with a 95% confidence interval of [29.1, 44.7] inches. 

side note; if want to check, put ?t.test in consol

#### Now, using in-line referncing 

mean otterlength is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1], 1)`,`r round(otter_ci$conf.int[2], 1)`] inches.

## Part 2: Two-sample t-tests

### Example 1

Make two mock samples, and ask the question: do we have sufficent evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean?

```{r}
#Make my mock samples
oak_trees <- c(20, 19, 24, 28, 34, 12, 15, 25)

pine_trees <- c(39, 26, 20, 30, 37, 22, 19, 18)

# Two-sample t-test
trees_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same 
# ie.; Trees are drawn from populations with the same mean height
#p-value is telling us that: If these are drawn from populations from the same mean, there's a 28.7% chance of getting samples that are at least this different. 
#if these samples are drawn from populations with the same mean height, then there is a 28% change of taking  ar random sample from each population and finding that the samples are at least this different from random chance.  --> not enough evidence to reject null hypothesis. (reject/null shoukdn;t jshow up in  reort)
```
The mean heights  of oak and pine trees were (X+- y) and (x=-Y), respectably and he difference was not significant (t(`r trees_t$parameter`) = `r round(trees_t$statistic,1)`, p=`r round(trees_t$p.value, 1)`)
"t(df) = t-statistic, p = p-value" 


*Avoid*: p=0

When things get really small  (ususally p<001)

*Not great* 



## Part 3: Another t-test with cars data 

### Take a look at the data 

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv")) 

#Check for remaining levels 
unique(compact_suv$class)
```
Create a histogram of gas mileage (cty) faceted by class starting from compact.suv

```{r}
ggplot(data = compact_suv, aes(x = cty)) +
  geom_histogram(bins=12) +
  facet_wrap(~class)

ggplot(data = compact_suv, aes(sample=cty)) +
  geom_qq() +
  facet_wrap(~class)


```
Might need to check ehich text you----
There are other things out there 

Find some sumary statiscts for each group 

```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>%
  summarize(
    mean_city = round(mean(cty), 2),
    sd_city = sd(cty),
    sample_size = n()
  )
  
```

The t.test function REALLY wants vectors of things.
`pull()` function to pull out a vector from a data frame.

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

#Your turn: do the same thing to get a vector of city gas milages for SUVS

suv_sample <- compact_suv %>% 
  filter(class=="suv") %>% 
  pull(cty)

```


Ho: Mean City gas milages fro SUVs and compact cars are the same 

```{r}
t.test(compact_sample, suv_sample)
```

There is a signifcant differnce in mean city gas milage for SUVs and compact cars (t(df)) = t-statistic, p < 0.001)


