---
title: "lab 5"
author: "Sam Rozal"
date: "10/25/2021"
output: 
  html_document: 
    toc: yes
    theme: cerulean
    code_folding: hide
---

```{r setup, include=FALSE, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals 

In this section, we'll use the `t.test()` function to calculate confidence intervals 

### Example 1

Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn to about in-line code referencing so our code becomes more reproducable 

```{r}
#create a mock sample
otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29)

#Find the confidence intervals:
otter_ci <- t.test(otter_lengths)

#find the standard Deviation 
otter_sd <- sd(otter_lengths)
```
What does confidence interval mean?
- We would expect if we took multiple samples from this pop and calculated a confidence interval for each othem we expect for 95% of the confidence intervals to contain the true population mean. 


Mean otter leangth is 36.9 inches $\pm$ (mean $\pm$ n=8) with a 95% confidence interval of [29.1, 44.7] inches. 

side note; if want to check, put ?t.test in consol

#### Now, using in-line referncing 

mean otterlength is `r round(otter_ci$estimate, 1)` inches.
